---
title: "flat_fetch_updated_data.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# fetch_updated_ambient_data

Thanks to the `ambientweatheR` package,
we can access all of the weather data from our ambient devices
in a standardized format. This makes use of the Ambient Weather API,
which we demonstrate below. Remember to set your API
key in the `.Renviron` file!

```{r}
#devtools::install_github("andrewflack/ambientweatheR")
library(ambientweatheR)
library(purrr)
library(dplyr)
```

First, we list our devices:

```{r}
list_user_devices() %>%
  flatten() %>%
  pluck("macAddress") -> device_id
```

Then fetch the data for the device:

```{r}
fetch_device_data(device_id) %>%
  pluck("content")
```

Easy peasy!

We define a function that fetches device data for an individual device:

```{r development-fetch_updated_ambient_data}
# Prepare the code of your function here
```

```{r function-fetch_updated_ambient_data}

#' Fetch Updated Ambient Weather Data
#'
#' Fetches device data from Ambient Weather for a date range. If `lookback` is
#' positive, data are fetched from `today - lookback` through today. Otherwise,
#' the function looks for the most recent date in `existing_db_path` and fetches
#' from that day forward (overwriting that day if it already exists).
#'
#' @param device_id Character scalar. Ambient Weather device ID.
#' @param lookback Numeric scalar. Number of days to look back from today.
#'   Use a positive value to fetch recent data; the default `-1` triggers
#'   fetching from the most recent date found in `existing_db_path`.
#' @param existing_db_path Character scalar. Path to existing parquet data
#'   (default: `here::here("data/ambient_processed")`).
#' @param api_key Character scalar. Ambient Weather API key. Defaults to
#'   `Sys.getenv("AMBIENT_WEATHER_API_KEY")`.
#'
#' @return A tibble with device data, sorted by `date_time`, with `device_id`
#'   appended as a column.
#'
#' @importFrom ambientweatheR fetch_device_data
#' @importFrom purrr pluck map_chr map_df
#' @importFrom dplyr as_tibble mutate arrange
#' @importFrom cli cli_alert_info cli_alert_danger cli_alert_success
#' @importFrom here here
#' @importFrom fs dir_exists
#' @importFrom arrow read_parquet
#'
#' @examples
#' \dontrun{
#' fetch_updated_ambient_data("C4:D8:D5:3B:4C:F9", lookback = 7)
#' }
#'
#' @export
fetch_updated_ambient_data <- function(api_key = Sys.getenv("AMBIENT_WEATHER_API_KEY"), device_id, lookback = -1, existing_db_path = here::here("data/ambient_processed")) {

  today <- Sys.Date()
  if (lookback > 1){
    # in this case, we want to fetch data starting from n days ago until today
    cli_alert_info("Fetching data from the last {lookback} days...")
    start_date <- as.POSIXct(today - lookback)
  
  } else {
    # in this case, we want to check the database for the most recent date we have data
    # for, and start fetching from there
    
    cli_alert_info("Checking most recent date in the database...")
    start_date <- as.POSIXct(today)
    
    if (dir_exists(existing_db_path)) {
      existing_data <- list.files(existing_db_path, recursive = TRUE, full.names = TRUE, pattern = "\\.parquet$") %>%
        map_dfr(read_parquet)
      
      if (nrow(existing_data) > 0) {
        most_recent_date <- max(existing_data$date_time)
        # floor to that day, so it automatically overwrites that day and fetches all data from that day onward
        start_date <- as.Date(most_recent_date)
        cli_alert_info("Most recent date in the database is {most_recent_date}. Fetching data starting from {start_date}...")
      } else {
        cli_alert_danger("No existing data found in the database.")
        stop("No existing data found in the database. Please provide a valid path to the existing database or set lookback to a positive number.")
      }
    } else {
      cli_alert_danger("No existing database found.")
      stop("No existing database found. Please provide a valid path to the existing database or set lookback to a positive number.")
    }
  }

  cli_alert_info("Fetching data starting from {start_date}...")
  seq.Date(from = as.Date(start_date), to = Sys.Date(), by = "days") %>%
    map_chr(as.character) %>%
    map_df(
      ~ fetch_device_data(device_id, .x) %>% 
        pluck("content") %>% 
        as_tibble()
      ) %>%
    mutate(device_id = device_id) %>%
    arrange(date_time) -> output_df
  
  cli_alert_success("Data fetching complete for device {device_id}. Retrieved {nrow(output_df)} records.")
  return(output_df)
}
```

```{r tests-fetch_updated_ambient_data}
test_that("fetch_updated_ambient_data works", {
  expect_true(inherits(fetch_updated_ambient_data, "function"))
})
```

# dump_ambient_to_disk

Once we have the data, we can dump it to disk:
    
```{r development-dump_ambient_to_disk}
# You can prepare the code of the dump_ambient_to_disk() function here
```
  
```{r function-dump_ambient_to_disk}
#' Dump Ambient Weather Data to Partitioned Parquet Files
#'
#' Partitions a data frame by date and device, creates a year/month/day folder
#' hierarchy under `output_path`, and writes one parquet file per
#' `year/month/day/device_id` group. Returns a character vector of all file
#' paths under the output directory.
#'
#' @param df A data frame or tibble containing a datetime column and `device_id`.
#' @param proj_root Character scalar. Project root used to build output paths.
#'   Defaults to `here::here()`.
#' @param output_path Character scalar. Relative path under `proj_root` where
#'   data are written (default: `"data/ambient_processed"`).
#' @param dt_col Bare column name for the datetime column used to derive
#'   `year`, `month`, and `day`. Defaults to `date_time`.
#'
#' @return Character vector of full file paths written under `output_path`.
#'
#' @importFrom dplyr mutate distinct group_by group_walk select
#' @importFrom purrr pwalk
#' @importFrom fs dir_create
#' @importFrom here here
#' @importFrom arrow write_parquet
#' @importFrom glue glue
#' @importFrom fs path
#'
#' @examples
#' \dontrun{
#' dump_ambient_to_disk(ambient_df, dt_col = date_time)
#' }
#'
#' @export
dump_ambient_to_disk <- function(
  df,
  proj_root = here::here(),
  output_path = "data/ambient_processed",
  dt_col = date_time
) {

  df <- df %>%
    mutate(
      dt = as.Date({{dt_col}}),
      year  = format(dt, "%Y"),
      month = format(dt, "%m"),
      day   = format(dt, "%d")
    )

  df %>%
    distinct(year, month, day) %>%
    pwalk(function(year, month, day) {
      dir_create(path(proj_root, output_path, year, month, day))
    })

  df %>%
    group_by(year, month, day, device_id) %>%
    group_walk(function(.x, .y) {

      .x %>%
        select(-dt) %>%
        write_parquet(
          .,
          path(proj_root, output_path, .y$year, .y$month, .y$day, glue("{.y$device_id}_ambient_data_{.y$year}{.y$month}{.y$day}.parquet"))
        )
    })

  return(list.files(path(proj_root, output_path), recursive = TRUE, full.names = TRUE))
}
```

```{r tests-dump_ambient_to_disk}
test_that("dump_ambient_to_disk works", {
  expect_true(inherits(dump_ambient_to_disk, "function")) 
})
```
  
# fetch_updated_airqo_data

In addition to our ambient weather data, we also want to fetch the most recent
data from AirQO, which is the organization that manages the air quality monitoring stations in Madagascar.

    
```{r development-fetch_updated_airqo_data}
# You can prepare the code of the fetch_updated_airqo_data() function here
```
  
```{r function-fetch_updated_airqo_data}
#' Title
#' 
#' Description
#' 
#' @return
#' 
#' @export
fetch_updated_airqo_data <- function(){
    
}
```
  
```{r example-fetch_updated_airqo_data}
fetch_updated_airqo_data()
```
  
```{r tests-fetch_updated_airqo_data}
test_that("fetch_updated_airqo_data works", {
  expect_true(inherits(fetch_updated_airqo_data, "function")) 
})
```
  

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_fetch_updated_data.Rmd", vignette_name = "Fetching Data from Ambient Weather API", check=FALSE, open=FALSE, clean=TRUE)
```

